Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-17 cloneoverflow-latex/cloneoverflow.tex
Latest update with stacked bar chart

\Cref{tab:stale_code} shows the findings of outdated clone investigation. The comparison with the clones' latest code reveals that there are 55 clone pairs that are outdated. These are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as accepted answers, and later have been changed during the development. \textit{hadoop} and \textit{spring} have the maximum number of 9 outdate code clones, followed by 6 clones from \textit{tomcat}, and 5 clones from \textit{eclipse-SDK}. An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after}. The newest version has one line added. We also found outdated code which contains more disruptive changes. The code snippet in Stack Overflow Post 23520731 which is a copy of \textit{SchemaUpdate.java} in \textit{hibernate} has been heavily modified (as shown in \Cref{fig:hibernate_outdated_code}). Moreover, there is a code snippet in Stack Overflow post 3758110 which is a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring. It was deleted in commit 02a4473c62d8240837bec297f0a1f3cb67ef8a7b by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted and the latest version of Spring does not contain the Java file anymore.

@@

\begin{table}
	\centering
	\caption{Breakdowns of findings from outdated code investigation of 96 category-A online clone pairs}
	\label{tab:stale_code}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Project & Pairs & Outdated & Fresh & Del. & Others \\
		\hline
		ant & 1 & 0 & 1 & 0 & 0 \\
		log4j & 4 & 0 & 4 & 0 & 0 \\
		tomcat & 7 & 7 & 0 & 0 & 0 \\
		aspectj & 2 & 2 & 0 & 0 & 0 \\
		eclipse-SDK & 12 & 5 & 7 & 0 & 0 \\
		hadoop & 14 & 9 & 5 & 0 & 0 \\
		hibernate & 16 & 4 & 11 & 1 & 0 \\
		jasperreports & 2 & 2 & 0 & 0 & 0 \\
		jfreechart & 4 & 4 & 0 & 0 & 0 \\
		jgraph & 5 & 4 & 0 & 0 & 1 \\
		jgrapht & 1 & 0 & 1 & 0 & 0 \\
		jstock & 2 &  2 & 0 & 0 & 0 \\
		jung & 2 & 2 & 0 & 0 & 0 \\
		junit & 3 & 3 & 0 & 0 & 0 \\
		poi & 3 & 1 & 2 & 0 & 0 \\
		spring & 14 & 9 & 3 & 2 & 0 \\
		struts & 1 & 1 & 0 & 0 & 0 \\
		weka & 3 & 0 & 3 & 0 & 0 \\
		\hline
		Total & 96 & 55 & 37 & 3 & 1 \\
		\hline
	\end{tabular} 
%}
\end{table}

@@

		\hline& 

>>>>

\Cref{fig:outdated} shows the findings of outdated clone investigation. The comparison with the clones' latest code reveals that there are 55 clone pairs that are outdated. These are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as accepted answers, and later have been changed during the development. \textit{hadoop} and \textit{spring} have the maximum number of 9 outdate code clones, followed by 6 clones from \textit{tomcat}, and 5 clones from \textit{eclipse-SDK}. An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after}. The newest version has one line added. We also found outdated code which contains more disruptive changes. The code snippet in Stack Overflow Post 23520731 which is a copy of \textit{SchemaUpdate.java} in \textit{hibernate} has been heavily modified (as shown in \Cref{fig:hibernate_outdated_code}). Moreover, there is a code snippet in Stack Overflow post 3758110 which is a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring. It was deleted in commit 02a4473c62d8240837bec297f0a1f3cb67ef8a7b by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted and the latest version of Spring does not contain the Java file anymore.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{outdated}
	\caption{Findings from outdated code investigation of 96 category-A online clone pairs}
	\label{fig:outdated}
\end{figure}

%\begin{table}
%	\centering
%	\caption{Breakdowns of findings from outdated code investigation of 96 category-A online clone pairs}
%	\label{tab:stale_code}
%	\small
%%	\resizebox{\columnwidth}{!}{%
%	\begin{tabular}{l|r|r|r|r|r}
%		\hline 
%		Project & Pairs & Outdated & Fresh & Del. & Others \\
%		\hline
%		ant & 1 & 0 & 1 & 0 & 0 \\
%		log4j & 4 & 0 & 4 & 0 & 0 \\
%		tomcat & 7 & 7 & 0 & 0 & 0 \\
%		aspectj & 2 & 2 & 0 & 0 & 0 \\
%		eclipse-SDK & 12 & 5 & 7 & 0 & 0 \\
%		hadoop & 14 & 9 & 5 & 0 & 0 \\
%		hibernate & 16 & 4 & 11 & 1 & 0 \\
%		jasperreports & 2 & 2 & 0 & 0 & 0 \\
%		jfreechart & 4 & 4 & 0 & 0 & 0 \\
%		jgraph & 5 & 4 & 0 & 0 & 1 \\
%		jgrapht & 1 & 0 & 1 & 0 & 0 \\
%		jstock & 2 &  2 & 0 & 0 & 0 \\
%		jung & 2 & 2 & 0 & 0 & 0 \\
%		junit & 3 & 3 & 0 & 0 & 0 \\
%		poi & 3 & 1 & 2 & 0 & 0 \\
%		spring & 14 & 9 & 3 & 2 & 0 \\
%		struts & 1 & 1 & 0 & 0 & 0 \\
%		weka & 3 & 0 & 3 & 0 & 0 \\
%		\hline
%		Total & 96 & 55 & 37 & 3 & 1 \\
%		\hline
%	\end{tabular} 
%%}
%\end{table}

@@
